\documentclass[main.tex]{subfiles}
\graphicspath{{\subfix{../images}}}
\begin{document}
\hbox{} Hello and prepare for the hardest two year (or if you're a sadist, one year) \textbf{course for a long while}! It's IB Math AA HL, the best course known to at least some portion of the human race!\\ This course is being written in \LaTeX. So please excuse the occasional mishap that occurs throughout the document.\\
Here is every formula given to you in the booklet. Don't throw this book into the rubbish bin out of sheer agony just yet, as I will go over \textsl{every} formula in this booklet as we progress through each topic. (except for the prerequisites, you should already know them from previous maths classes) By the end of this (hopefully) small book, you should be able to understand a large portion of IB Math AA HL.\footnote{This does NOT mean you can skip buying a textbook! Try getting the books that are in the ``Further Reading'' section.} However, it is up to \textsl{you} to get a 7 on the exam. You need to study very hard in order to get a high achieving score.\\

\begin{center}
 You can find the Analysis and Approaches Formula Booklet \href{https://bit.ly/maaformulabooklet}{here}.\\
\end{center}
\subsection*{\textsl{I'm currently a Math AA SL student, and this seems pretty cool. How can I join AA HL?}}

Well, first off I would suggest meeting with your coordinator to discuss about possibly going up to HL. There is about 90 extra teaching hours of content to go through for HL. Depending on how your IB School structures their maths courses, it may be possible to go from one level to another as AA SL is a subset of AA HL. (If you don't know what a \textsl{subset} is, we'll discuss it in Topic 4.) 

\subsection*{\textsl{What's the point of this PDF?}}

I made this document to assist people who are going to take the IB Math AA HL exam, which began examination in May 2021 and ends in May 2028\footnote{It's just a somewhat random guess, I think they change it every 7 or so years.}, but do not have a proper HL course.\\
e.g:  Combined SL and HL classes or an HL class doesn't exist, but is available for examination.
\newpage

Alright, assuming you have chosen this course and accepted the consequences of life, you may be asking yourself,
\begin{center}How is this ``class" even structured?\end{center}

 Based off of what IB recommends, SL AA should have about 150 hours of teaching. However, HL AA has an extra 90 additional hours of content. Although it is not necessary for SL students to read through this HL document, it may be worth reading for enrichment.
 
 This document, which only goes over the \textbf{HL} content, should be completed in around 6 months for those that recently finished the SL content or \textbf{10} months for those who are reading this document along with an SL class.
\end{document}